Probabilities of polar aligned disks in binary star systems

### 2024-04-17 src/tex/ms.tex
Describe example simulation in the text

Figure \ref{fig:sim_example} shows a set of example simulations along with their determined states. \RGM{describe parameters of the system, masses, eccentricity etc} Visualizing the 
system in this way makes it clear why we have chosen our two criteria. Librating orbits will never cross the x-axis
and will cause the polar angle ($\Omega$) to turn back before reaching $0$ or $\pi$. Precessing orbits (both prograde and retrograde)
travel approximately in circles with near-constant $i$.

>>>>

Figure \ref{fig:sim_example} shows a set of example simulations along with their determined states.
These simulations all consist of a central $1 M_\odot$ binary of equal mass stars in an orbit with $a=0.2$ and $e=0.4$.
A massless third body is orbiting at a distance of $a=1$.
Visualizing the system in this way makes it clear why we have chosen our two criteria. Librating orbits will never cross the x-axis
and will cause the polar angle ($\Omega$) to turn back before reaching $0$ or $\pi$. Precessing orbits (both prograde and retrograde)
travel approximately in circles with near-constant $i$.
